### 2018-11-02 paper/complexity.tex
Extended calculation for complexity theorem.

\item For $j > \#\ol s$, one execution is won by entering 
branch (\ref{eq:ufb}) after $\ol s$, no executions are lost.
\end{enumerate}
%
Summing up over all test cases for $j=0,\dots,pq-1$, the difference in test executions generated
from $Z(\ol s)$ and those generated from  $Z$ is
\begin{equation}
 pq - \#\ol s       - \card{\minhits(Z/\ol s)}.
\end{equation}
%
This expression is maximal for $\card{\minhits(Z/\ol s)} = 1$ (recall that
the definition of $Z(\ol s)$ requires $\card{\minhits(Z/\ol s)} > 0$). 
The number of hitting sets in $\minhits(Z/\ol s)$ is one if and only if the
minimal acceptances of $Z/\ol s$ have exactly one element in their common intersection.
The maximal length of 
$\ol s$ where the expression remains strictly positive is then $pq - 2$.

@@

Summing up over all test cases ${\ol U}_F(j),\ j = \ol j,\dots,pq-1$, for a given 
 $k \le \card{\Sigma}^{\ol j}$, this results in 
an upper bound of
\begin{equation}
 \card{\Sigma}^{\ol j}(pq - \ol j      - 1)
\end{equation}
additional test executions in comparison to the number of executions needed for all tests
of $Z$. The maximal value of this term is reached for $\ol j = pq - 2$: this is the maximal exponent where $(pq - \ol j      - 1)$ is still greater than zero. We conclude that the
maximal increase of test executions to be gained if processes possess failures $(s,\Sigma)$
is of the order $\card{\Sigma}^{pq - 2}$. This can be neglected in comparison to 
the worst case applicable for processes that do not possess any failures $(s,\Sigma)$, because 
formula (\ref{eq:maxO}) shows that the number of test executions required for the latter   is of order $\card{\Sigma}^{pq - 1}$.

These considerations lead to the following theorem
%
\begin{theorem}
Given a process alphabet $\Sigma$ with cardinality $
\card{\Sigma} = n$, consider a fault model ${\cal F} = (P,\lessdet_F,{\cal D})$, such that
the normalised transition graph of $P$ has $p$ states, and the fault domain 
${\cal D}$ contains all processes $Q$ over alphabet $\Sigma$, such that $G(Q)$ has at most $q$ states. Then the maximal 
number of test executions to be performed   using the complete test 
suite $\TS_F = \{ U_F(j)~|~0 \le j < pq  \}$ created from $P$ as specified in Theorem~\ref{th:failurestest} is of order
%
\begin{equation*} 
O\big(\binom{n}{\lfloor\frac{n}{2}\rfloor}\cdot n^{pq-1}\big)\quad\text{with $n=\card{\Sigma}$}.
\end{equation*} 
\xbox
\end{theorem}
%
In~\cite{Hennessy:1988:ATP:50497}, it is suggested to test {\it every}
non-empty subset of $\Sigma$ whose events cannot be completely refused in a
given process state of the reference model; this leads to a worst-case
estimate of $2^{\card{\Sigma}}-1$ for the number of different sets to be
offered to the SUT in the last step of the test execution. This number is significantly larger than the worst-case estimate $\binom{n}{\lfloor n/2\rfloor}$ calculated above for the 
hitting sets to be checked.
In Fig.~\ref{fig:minhita}, the reduction is visualised by plots of
the two functions.

@@

% .....................................................................................
 \begin{figure}
 %%\hspace*{-40mm}
 \begin{center}
\includegraphics[width=.8\textwidth]{curvecomparison.pdf}
\end{center}
%\vspace*{-10mm}
\caption{Function plot $2^{\card{\Sigma}}$ versus $\frac{2^\card{\Sigma}}{\sqrt{2\pi \card{\Sigma}}}$.}
 \label{fig:minhita}
 \end{figure}
% .......................................................................................

>>>>

\item For $j > \#\ol s$, one execution is won by entering 
branch (\ref{eq:ufb}) after $\ol s$, no executions are lost.
\end{enumerate}
%
Summing up over all test cases for $j=0,\dots,pq-1$, the difference in test executions generated
from $Z(\ol s)$ and those generated from  $Z$ is
\begin{equation}
 pq - \#\ol s       - \card{\minhits(Z/\ol s)}.
\end{equation}
%
This expression is maximal for $\card{\minhits(Z/\ol s)} = 1$ (recall that
the definition of $Z(\ol s)$ requires $\card{\minhits(Z/\ol s)} > 0$). 
The number of hitting sets in $\minhits(Z/\ol s)$ is 1, for example, if   the
minimal acceptances of $Z/\ol s$ have exactly one element in their common intersection.
The maximal length of 
$\ol s$ where the expression remains strictly positive is then $pq - 2$.

@@

Summing up over all test cases ${\ol U}_F(j),\ j = \ol j,\dots,pq-1$, for a given 
 $k \le \card{\Sigma}^{\ol j}$, this results in 
an upper bound of
\begin{equation}
 \card{\Sigma}^{\ol j}(pq - \ol j      - 1)
\end{equation}
additional test executions in comparison to the number of executions needed for all tests
of $Z$.

So far, the additional executions originating from traces with fixed length $\ol j\in\{0,\dots,pq-2\}$ have been considered. Summing up over all lengths $\ol j$ results in
an upper bound of 
%
\begin{equation}
\sum_{j=0}^{pq-2} n^j(pq - j - 1) = \frac{n^{pq} - npq + pq - 1}{(n-1)^2}\quad\text{with}\ 
n=\card{\Sigma}
\end{equation}
%
additional test executions. This has the order of magnitude $O(n^{pq-2})$. Therefore, the additional test executions won by being able to enter branches (\ref{eq:ufb}) in test executions  can be neglected in comparison to the order of magnitude calculated for $\pmax$ in (\ref{eq:maxO}).  
These considerations lead to the following theorem
%
\begin{theorem}
Given a process alphabet $\Sigma$ with cardinality $
\card{\Sigma} = n$, consider a fault model ${\cal F} = (P,\lessdet_F,{\cal D})$, such that
the normalised transition graph of $P$ has $p$ states, and the fault domain 
${\cal D}$ contains all processes $Q$ over alphabet $\Sigma$, such that $G(Q)$ has at most $q$ states. Then the maximal 
number of test executions to be performed   using the complete test 
suite $\TS_F = \{ U_F(j)~|~0 \le j < pq  \}$ created from $P$ as specified in Theorem~\ref{th:failurestest} is of order
%
\begin{equation*} 
O\big(\binom{n}{\lfloor\frac{n}{2}\rfloor}\cdot n^{pq-1}\big)\quad\text{with $n=\card{\Sigma}$}.
\end{equation*} 
\xbox
\end{theorem}
%
In~\cite{Hennessy:1988:ATP:50497}, it is suggested to test {\it every}
non-empty subset of $\Sigma$ whose events cannot be completely refused in a
given process state of the reference model; this leads to a worst-case
estimate of $2^{\card{\Sigma}}-1$ for the number of different sets to be
offered to the SUT in the last step of the test execution. This number is significantly larger than the worst-case estimate $\binom{n}{\lfloor n/2\rfloor}$ calculated above for the 
hitting sets to be checked.
In Fig.~\ref{fig:minhita}, the reduction is visualised by plots of
the two functions.

@@

% .....................................................................................
 \begin{figure}
 %%\hspace*{-40mm}
 \begin{center}
\includegraphics[width=.8\textwidth]{curvecomparison.pdf}
\end{center}
%\vspace*{-10mm}
\caption{Function plot $2^{\card{\Sigma}}$ versus $\binom{n}{\lfloor \frac{n}{2}\rfloor}$.}
 \label{fig:minhita}
 \end{figure}
% .......................................................................................
